Penalized linear mixed models for structured genetic data

### 2021-03-19 main.tex
fixing typo in 5, using enfloat

To quantify selection accuracy, we calculated the precision according to $\#\{ \beta > 0 \cap \widehat{\beta} > 0  \}/\#\{ \widehat{\beta} \ne 0 \}$ in order to ensure SNPs were not only selected, but the direction of effect was estimated correctly (in our example, all causal $\beta$ values were positive). Figure~\ref{fig:gw_prc_mse}(a) displays each method's precision ($1 -$ the false discovery rate) for the corresponding number of selected SNPs. PC-lasso and LMM-lasso consistently outperform the ordinary lasso in selecting causal SNPs, particularly over the first $\approx$ 100 SNPs allowed into the model. For the most part, PC-lasso outperforms LMM-lasso in this setting as well. None of the methods are able to accurately select more than a few causal SNPs with this sample size.  However, because the ordinary lasso does not account for environmental confounding, it cannot reliable select \emph{any} SNPs: the first 38 SNPs selected were all false positives.

>>>>

To quantify selection accuracy, we calculated the precision according to $\#\{ \beta > 0 \cap \widehat{\beta} > 0  \}/\#\{ \widehat{\beta} \ne 0 \}$ in order to ensure SNPs were not only selected, but the direction of effect was estimated correctly (in our example, all causal $\beta$ values were positive). Figure~\ref{fig:gw_prc_mse}(a) displays each method's precision ($1 -$ the false discovery rate) for the corresponding number of selected SNPs. PC-lasso and LMM-lasso consistently outperform the ordinary lasso in selecting causal SNPs, particularly over the first $\approx$ 100 SNPs allowed into the model. For the most part, PC-lasso outperforms LMM-lasso in this setting as well. None of the methods are able to accurately select more than a few causal SNPs with this sample size.  However, because the ordinary lasso does not account for environmental confounding, it cannot reliably select \emph{any} SNPs: the first 38 SNPs selected were all false positives.
